---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/pollsDK)](http://cran.r-project.org/package=pollsDK)


# pollsDK

The goal of pollsDK is to make it easy to download and use danish polling data.

## Installation

You can install pollsDK from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("mikkelkrogsholm/pollsDK")
```

## Load library
```{r message=FALSE, warning=FALSE}
library(pollsDK); library(tidyverse)
```

## Gahner
The package owes a lot to [Erik Gahner](https://github.com/erikgahner) whos github repo [polls](https://github.com/erikgahner/polls) is a plethora of polling data.

#### `get_gahner()`
```{r get_gahner, message=FALSE, warning=FALSE}
## Collects poll data from Erik Gahners Github

g <- get_gahner()

glimpse(g)
```

## Berlingske and Ritzau
You can also pull the polls from Berlingske Barometer and Ritzau Index

#### `get_berlingske()`
```{r get_berlingske, message=FALSE, warning=FALSE}
# Get the Berlingske Barometer

b <- get_berlingske()

glimpse(b)
```

#### `get_polls()`
```{r get_polls, message=FALSE, warning=FALSE}
# Get polls from Berlingske

p <- get_polls()

glimpse(p)
```

For both `get_polls()` and `get_berlingske()` it will pull polls from the current year. You can change that by supplying it with the year argument.
```{r berlingske_2014, message=FALSE, warning=FALSE}
# And even from previous years

p14 <- get_polls(2014)

glimpse(p14)
```

#### `get_ritzau()`
Ritzau provides a list of data frame with the most recent polls from a select number of pollsters. Each one hase the pollsters number and Ritzaus own index.
```{r get_ritzau}
# Get Ritzau data

r <- get_ritzau()

glimpse(r[[1]])
```

