---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
library(pollsDK)
```

[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/pollsDK)](http://cran.r-project.org/package=pollsDK)


# pollsDK

The goal of pollsDK is to make it easy to download and use danish polling data.

## Installation

You can install pollsDK from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("56north/pollsDK")
```

## Gahner

The package owes a lot to [Erik Gahner](https://github.com/erikgahner) whos github repo [polls](https://github.com/erikgahner/polls) make many of the functions in this package possible.

There are four gahner_ functions in this package:

#### `gahner`
```{r gahner, message=FALSE, warning=FALSE}
## Collects poll data from Erik Gahners Github

polls <- gahner()

polls

```

#### `gahner_partyletters` and `gahner_pollingfirms`
```{r gahner_helper, message=FALSE, warning=FALSE}
## Tells you which parties and  which polling firms are in Gahners data

gahner_partyletters()

gahner_pollingfirms()
```

#### `gahner_plot`
```{r gahner_plot, message=FALSE, warning=FALSE}
## Visualizes poll data from Erik Gahners Github

gahner_plot()
```

You can filter the `gahner_plot()` by telling it which parties or polling firms you want to include in the plot.

```{r gahner_plot2, message=FALSE, warning=FALSE}
## Visualizes poll data from Erik Gahners Github, but filter to only include "I" (Liberal Alliance).


gahner_plot(parties = "I")
```

## Berlingske and Ritzau
You can also pull the polls from Berlingske Barometer and Ritzau Index

#### `berlingskebarometer`
```{r berlingske, message=FALSE, warning=FALSE}
# Get information from Berlingske Barometer

berlingskebarometer()
```

```{r berlingske_2014, message=FALSE, warning=FALSE}
# And even from previous years

berlingskebarometer(2014)
```

#### `ritzauindex`
Ritzau provides a list of data frame with the most recent polls from a select number of pollsters. Each one hase the pollsters number and Ritzaus own index.
```{r}
# Get Ritzau data

ritzau <- ritzauindex()

ritzau[[1]]
```

